Data Specialization for a Staged Lambda Calculus

### 2015-02-28 paper/splitting.tex

\paragraph {Injections.}
Now consider splitting the non-terminal, $\inl {e}$, where $\diaone
{e} \xi v$ and $\rtab \xi v \vsplito \mval i q$. Therefore:
\[
	\splitone e A c {l.r} \text{ and } \reduce c {\tup{i,b}} \text{ and } [b/l]r \equiv q
\]
Since $\diaone {\inl e} \xi {\inl v}$ and $\rtab \xi {\inl v} \vsplito \mval {\inl i} q$,
splitting must produce a $c'$ and $l.r'$ satisfying,
\[
	\reduce {c'} {\tup{\inl i,b'}} \text{ and } [b'/l]r' \equiv q
\]
Our algorithm generates a first-pass term $c'$ that produces the same
boundary value as splitting $e$:
\[
c' = \letin {\tup {x,y}} c {\tup{\inl x, y}}
\]
Splitting the injection also generates the same resumer as splitting
the subterm $e$: ($l.r' = l.r$).

@@

\paragraph {Function.} 
Function introduction has a $\tup{}$ boundary value, since functions
are already fully reduced in our semantics.  However, since the body
of a function may itself be multistage, splitting must continue into
it.  The first-pass term generate by split produces an $i$ that is a
new function formed from the first-stage part of the original body.
The resumer is a new function formed out of the second-stage part of
the original body.  It is the responsibility of the application site
to save the precomputation of the function body and pass it to the
resumer version of the function.

>>>>

\paragraph {Injections.}
Now consider splitting the non-terminal, $\inl {e}$, where $\diaone
{e} \xi v$ and $\rtab \xi v \vsplito \mval i q$. Therefore:
\[
	\splitone e A c {l.r} \text{ and } \reduce c {\tup{i,b}} \text{ and } [b/l]r \equiv q
\]
Since $\diaone {\inl e} \xi {\inl v}$ and $\rtab \xi {\inl v} \vsplito \mval {\inl i} q$,
splitting must produce a $c'$ and $l.r'$ satisfying,
\[
	\reduce {c'} {\tup{\inl i,b'}} \text{ and } [b'/l]r' \equiv q
\]
Our algorithm generates a first pass $c'$ that produces the same
boundary value as splitting $e$:
\[
c' = \letin {\tup {x,y}} c {\tup{\inl x, y}}
\]
Splitting the injection also generates the same resumer as splitting
the subterm $e$: ($l.r' = l.r$).

@@

\paragraph {Function.} 
Function introduction has a $\tup{}$ boundary value, since functions
are already fully reduced in our semantics.  However, since the body
of a function may itself be multistage, splitting must continue into
it.  The first pass generated by split produces an $i$ that is a new
function formed from the first-stage part of the original body.  The
resumer is a new function formed out of the second-stage part of the
original body.  It is the responsibility of the application site to
save the precomputation of the function body and pass it to the
resumer version of the function.
